\newpage
\section{Conclusion}
The mass of the $Z^0$ boson could be determined with high accuracy
\begin{equation*}
	M_Z=\unit{(91.188\pm0.008)}{GeV}
\end{equation*}
and matches the literature value $M_z^{lit}=\unit{91.187}{GeV}$ within its $1\sigma$ interval.\\
The total decay width $\Gamma_Z$ of the $Z^0$ decay channel was calculated as
\begin{equation*}
\Gamma_Z=\unit{(2.516\pm0.017)}{GeV}
\end{equation*}
which includes $\Gamma_Z^{lit}=\unit{2.4862}{GeV}$ in its $2\sigma$ margin. The error in the decay width largely originates from the efficiency matrix, which was calculated at using the simulated data. The simulations were done at $\sqrt{s}\approxeq\unit{91.3}{GeV}$, which is roughly the resonance energy of the $Z^0$ decay. The actual efficiencies of the applied cuts might vary for the off-resonance data points, thus causing the discrepancy in the decay widths.
Perhaps for the same reason, the expected results assuming lepton universality could not be reproduced. The partial decay widths of the lepton events calculated by the authors were 
\begin{equation*}
\begin{aligned}
\Gamma_{e^+e^-}&=\unit{(94\pm4)}{MeV}\\
\Gamma_{\mu^+\mu^-}&=\unit{(82.9\pm1.7)}{MeV}\\
\Gamma_{\tau^+\tau^-}&=\unit{(76.9\pm1.9)}{Mev}
\end{aligned}
\end{equation*}
These results only match within multiples of their $\sigma$ intervals, meaning that the results neither confirm nor obviate lepton universality. The muon result was the only to include the expected lepton decay width of $\Gamma_l^{lit}=\unit{83.8}{MeV}$ \cite{staatsex} and was used to calculate the quark decay width from the fit results as $\Gamma_{q\overline{q}}=\unit{(1777\pm41)}{MeV}$. The literature value $\Gamma_{q\overline{q}}^{lit}=\unit{1732}{MeV}$ is slightly outside the $1\sigma$ interval.

Using these results the number of neutrino generations was estimated from the blind decay width $\Gamma_{blind}=\unit{(0.49\pm0.04)}{GeV}$ to be $n_\nu=(2.93\pm0.26)$. This leaves all integers but 3 outside of the $3\sigma$ margin, thus confirming the number of neutrino generations predicted by the Standard Model.