\documentclass[11pt, paper=a4]{scrartcl}

% CONFIG
\newcommand{\exptitle}{Z0 Resonance}       % long name of experiment 
\newcommand{\exptitleshort}{Z0} % short name of experiment
\newcommand{\expdate}{26.03.2016}           % date of experiment
\newcommand{\exptutor}{Christian L\"udtke}

\input{Vorspann}


\pagenumbering{Roman}
\setcounter{page}{1}


\input{abstract}
\tableofcontents

\newpage
\listoffigures
\thispagestyle{empty}

\newpage

\listoftables

\thispagestyle{empty}





\newpage
\hypersetup{pageanchor=false} %stop page numbering (hyperref) to prevent for double page numers

\clearpage
\pagenumbering{arabic}
\setcounter{page}{1}

\input{physicalprinciples}

\input{analysis}


\newpage
\begin{thebibliography}{9}
	\bibitem{staatsex}
	"Analyse von Z$^0$ Zerfällen." Albert-Ludwig University of Freiburg, Freiburg, Feb. 9 1995.
	\bibitem{anleitung}
	"Anleitung des Versuches \emph{$Z^0$-Resonanz}.", Albert-Ludwig University of Freiburg, Freiburg, Mar. 2 2012.
	\bibitem{binpaper}
	Paterno, Marc. "Calculating efficiencies and their uncertainties." FNAL/CD/CEPA/SLD, May 5, 2003. Access date: http://home.fnal.gov/~paterno/images/effic.pdf (April 21 2016 13:00.)
	\bibitem{muenchen}
	"Analyse von Z$^0$ Zerfällen." Ludwig-Maximilian University of Munich, Munich, Oct. 14 2010.
	\bibitem{Grif}
	Griffiths, David. "Einführung in dei Elementarteilchenphysik." Berlin: Akademischer Verlag, 1996 (Orig.: "Introduction to Elementary Particles". New York 1987.)
	\bibitem{jakobs}
	Jakobs, Karl. "Experimentalphysik V - 11. Experimentelle Tests der
	elektroschwachen Wechselwirkung". https://portal.uni-freiburg.de/jakobs/dateien/vorlesungsdateien/ex5-14/kap11 (22.04.2016)
	\bibitem{uni zuerich}
	Universität Zürich. Standard Model. http://www.physik.uzh.ch/groups/serra/StandardModel.html (23.04.2016)
\end{thebibliography}
\newpage
\appendix
\input{calculation}
\end{document}
